Location and Scale-Invariant Power Transformations for Transforming Data to

### 2024-09-19 manuscript_rmarkdown/manuscript.Rmd
Further work on transition to LaTeX.

---
title: "Location and Scale-Invariant Power Transformations for Transforming Data to
  Normality"
author: "Alex Zwanenburg, Steffen Löck"
date: "`r Sys.Date()`"
output:
  pdf_document:
    latex_engine: lualatex
papersize: a4
bibliography: refs.bib
header-includes:
- \usepackage{amsmath}
- \usepackage{booktabs}
- \DeclareMathOperator*{\argmax}{argmax}
- \DeclareMathOperator*{\argmin}{argmin}
- \DeclareMathOperator{\sgn}{sgn}
---

>>>>

---
title: "Location and Scale-Invariant Power Transformations for Transforming Data to
  Normality"
author: "Alex Zwanenburg, Steffen Löck"
date: "`r Sys.Date()`"
output:
  pdf_document:
    latex_engine: lualatex
    keep_tex: true
papersize: a4
bibliography: refs.bib
header-includes:
- \usepackage{amsmath}
- \usepackage{booktabs}
- \DeclareMathOperator*{\argmax}{argmax}
- \DeclareMathOperator*{\argmin}{argmin}
- \DeclareMathOperator{\sgn}{sgn}
---
